Detecting diversifying selection for a trait from within and between-species genotypes and phenotypes

### 2024-07-05 manuscript/main.tex
Changes suggested by editor in pp of diversifying selection

For mammalian body and brain mass, we obtained male (\Male) and female (\Female) trait variations.
Combined with nucleotide diversity and divergence, we estimated $\NI$ and posterior probabilities of diversifying selection under different assumptions for trait heritability as shown in the Table~\ref{table:empirical}.
Assuming complete heritability, body mass was found to be under diversifying selection with posterior probabilities of $0.0$ for both males and females.
If we assumed that heritability ($\Heritability$) of body mass was uniformly distributed between 20\% and 40\%~\citep{hu_bringing_2022}, posterior probabilities of diversifying selection became $0.635$ for males and $0.324$ for females.
Mammalian brain mass was found to be under diversifying selection with posterior probabilities of $0.877$ for males and $0.972$ for females when complete heritability was assumed.
Assuming a uniform distribution between 20\% and 40\% for heritability led to posterior probabilities of diversifying selection of $1.0$ for both males and females.

We also analyzed a similar dataset for body mass focusing this time only at Primates (Table~\ref{table:empirical}).
For primates body mass, assuming complete heritability, body mass was found to be under diversifying selection with posterior probabilities of $0.0$ for both males and females, exactly as in the mammal dataset.
However, we found posterior probabilities of diversifying selection of $1.0$ for males and $0.914$ for females when assuming a uniform distribution for the heritability of body mass between 20\% and 40\%.
For brain mass, assuming complete heritability or not (between 20\% and 40\%) did not change the posterior probability of diversifying selection, which was $1.0$.
Evidence for diversifying selection on both brain and body mass was therefore more pronounced in Primates than in mammals.
However, the genetic markers used to normalize trait variance with nucleotide divergence were not necessarily neutral, which could create spurious false positives by artificially inflating $\NI$ (Table~\ref{table:assumptions} and methods).

>>>>

For mammalian body and brain mass, we obtained male (\Male) and female (\Female) trait variations.
Combined with nucleotide diversity and divergence, we estimated $\NI$ and posterior probabilities of diversifying selection under different assumptions for trait heritability as shown in the Table~\ref{table:empirical}.
For body mass, assuming complete heritability led to zero posterior probabilities of diversifying selection for both males and females ($\proba [\NI > 1 ] = 0.0$).
If we assumed that heritability ($\Heritability$) of body mass was uniformly distributed between 20\% and 40\%~\citep{hu_bringing_2022}, posterior probabilities of diversifying selection became $0.635$ for males and $0.324$ for females.
Mammalian brain mass was found to be under diversifying selection with posterior probabilities of $0.877$ for males and $0.972$ for females when complete heritability was assumed.
Assuming a uniform distribution between 20\% and 40\% for heritability led to posterior probabilities of diversifying selection of $1.0$ for both males and females.

We also analyzed a similar dataset for body mass focusing this time only at Primates (Table~\ref{table:empirical}).
For primates body mass, assuming complete heritability led to zero posterior probabilities of diversifying selection for both males and females, exactly as in the mammal dataset.
However, we found posterior probabilities of diversifying selection of $1.0$ for males and $0.914$ for females when assuming a uniform distribution for the heritability of body mass between 20\% and 40\%.
For brain mass, assuming complete heritability or not (between 20\% and 40\%) did not change the posterior probability of diversifying selection, which was $1.0$.
Evidence for diversifying selection on both brain and body mass was therefore more pronounced in Primates than in mammals.
However, the genetic markers used to normalize trait variance with nucleotide divergence were not necessarily neutral, which could create spurious false positives by artificially inflating $\NI$ (Table~\ref{table:assumptions} and methods).
